Flabby and injective objects in toposes

### 2018-10-03 paper-flabby-objects.tex
typo

\item There is a way of embedding any module into a flabby module if one is
prepared to ignore set-theoretical difficulties. Namely, let~$M$ be an~$R$-module.
Inductively construct a collection~$T$ of terms by the following clauses: $0
\in T$ (where~$0$ is a formal symbol);
if~$t,s \in T$, then~$t + s \in T$; if~$t \in T$ and~$r \in R$, then~$rt \in
T$; if~$x \in M$, then~$\underline{x} \in T$; if~$K \subseteq T$ is a
subterminal, then~$\varepsilon_K \in T$. Let~$({\sim})$ be
the finest equivalence relation on~$T$ such that~$t + (s + u) \sim (t + s) +
u$, $t + s \sim s + t$, $t + 0 \sim t \sim 0 + t$, $1t \sim t$, $r(t+s) \sim rt
+ rs$, $(r+r')t \sim rt + r't$ and such
that~$\underline{0} \sim 0$, $\underline{x+y} \sim \underline{x} + \underline{y}$, $\underline{rx} \sim
r \underline{x}$, and such that~$\varepsilon_{\{t\}} \sim
t$ for all terms~$t$. Then the quotient~$T/{\sim}$ is a flabby~$R$-module
into which~$M$ embeds. However, it is not clear that~$T/{\sim}$ is a set.

>>>>

\item There is a way of embedding any module into a flabby module if one is
prepared to ignore set-theoretical difficulties. Namely, let~$M$ be an~$R$-module.
Inductively construct a collection~$T$ of terms by the following clauses: $0
\in T$ (where~$0$ is a formal symbol);
if~$t,s \in T$, then~$t + s \in T$; if~$t \in T$ and~$r \in R$, then~$rt \in
T$; if~$x \in M$, then~$\underline{x} \in T$; if~$K \subseteq T$ is a
subterminal, then~$\varepsilon_K \in T$. Let~$({\sim})$ be
the finest equivalence relation on~$T$ such that~$t + (s + u) \sim (t + s) +
u$, $t + s \sim s + t$, $t + 0 \sim t \sim 0 + t$, $0t \sim 0$, $1t \sim t$, $r(t+s) \sim rt
+ rs$, $(r+r')t \sim rt + r't$ and such
that~$\underline{0} \sim 0$, $\underline{x+y} \sim \underline{x} + \underline{y}$, $\underline{rx} \sim
r \underline{x}$, and such that~$\varepsilon_{\{t\}} \sim
t$ for all terms~$t$. Then the quotient~$T/{\sim}$ is a flabby~$R$-module
into which~$M$ embeds. However, it is not clear that~$T/{\sim}$ is a set.
